Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-15 manuscript.tex
refresh plotter

\title{
  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
} %% Article title

@@

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints. A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints. The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
\end{abstract}

@@

%% Keywords
\begin{keyword}
Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep Euler-Lagrange system \sep input constraint

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,m]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

@@

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
    %, enabling more precise real-time adaptation.
\end{itemize}

@@

The remainder of this paper is organized as follows. 
Section \ref{sec:Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Candidates of input constraints are presented in \ref{sec:appen:cstr}.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
% The appendices provide the proof of the lemma used in the stability analysis.

%  SECTION PROBLEM FORMULATION ============================
\section{Problem Formulation}\label{sec:Problem Formulation}

@@

The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model. The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure}

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

%  SECTION SIMULATION ======================================
\section{Implementation and Validation}\label{sec:sim}

The proposed CoNAC was validated via numerical simulation and real-time experiment on a two-link manipulator.

\subsection{Numerical Simulation Validation}

% ------------------------------------
% MCU & Robot Model and Ref. Trajectory
% ------------------------------------
The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
\MSRY{CORRECT HERE}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.

@@

% ------------------------------------
% Controllers: CoNAC 
% ------------------------------------
\subsubsection*{Controller 1: (C$_1$) CoNAC; proposed}

To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    c_{\overline\tau_2}     
    =
    \tau_2-\overline\tau_2
    \le 0
    ,
    \;
    c_{\underline\tau_2} 
    =
    \underline\tau_2-\tau_2
    \le 0
    ,
    \;
    c_{\rbu}
    =
    \tfrac{1}{2}
    (
        \norm{\rbu}-\overline\tau
    )^2 
    <0
    ,
    \label{eq:sim:cstr:CoNAC}
\end{equation}
where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.

@@

% ------------------------------------
% Controllers: Aux. system in CoNAC-AUX
% ------------------------------------
\subsubsection*{Controller 2: (C$_2$) CoNAC with auxiliary system}

@@

% ------------------------------------
% Controllers: CoNAC with small beta
% ------------------------------------
\subsubsection*{Controller 3: (C$_3$) CoNAC with small $\beta_i$}

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the further real-time implementation, and $1000$ Hz for the simulation.
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints. 
The readers are referred to the previous papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to address the weight constraints.

@@

% ------------------------------------
% Parameter Variation 
% ------------------------------------
% \begin{figure}[!t]      
%     \centering
%     {\includegraphics[width=\figSizeOneCol\linewidth]{
%         src/measurement/figures/Fig11.eps
%     }}
% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
%     \label{fig:ctrl:result:var}
% \end{figure}

% \begin{table}[!t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
%     \centering
%     \begin{tabular}{c c c c}
%     \hline
%         \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
%     \hline
%     \hline
%     \textbf{CoNAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
%     \hline
%     \textbf{CoNAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
%     \hline
%     \end{tabular}
%     \label{table:ctrl:result:var}
% \end{table}

% ------------------------------------
% Controller Parameters
% ------------------------------------
% \begin{table}[t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Parameters of the controllers used in simulation}
%     \label{table:controller:params}
%     \centering
%     \begin{tabular}{c | c c c c c c c c c c c c c c}
%     \hline
%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
%     \hline
%     \hline
%         \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
%     % \hline
%         \bf{CoNAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
%     \hline
%     \end{tabular}
% \end{table}

@@

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about 
$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CoNAC was demonstrated.

@@

The tracking performance of CoNAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.

@@

\subsection{Real-time Experiment Validation}

To validate the effectiveness of the proposed CoNAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\color{red}
The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
The reference trajectory was generated using the same method as in the numerical simulation.
\color{black}
The equal reference trajectory was applied and the parameters of the CoNAC were set to those whose best performance was achieved in the simulation (\ie $\beta=...$).
Additionally, the computational time was measured to validate the effectiveness of the proposed CoNAC in real-time applications.

>>>>

\title{
  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints 
} %% Article title

@@

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for weight norm and convex input constraints. 
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while addressing both types of constraints. 
  The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
  Real-time implementation was conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
\end{abstract}

@@

%% Keywords
\begin{keyword}
Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep input constraint

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

@@

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
    % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
    %, enabling more precise real-time adaptation.
\end{itemize}

@@

The remainder of this paper is organized as follows. 
Section \ref{sec:Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A real-time implementation of the proposed controller is presented in Section \ref{sec:sim}, where the proposed controller is applied to a 2-DOF robotic manipulator.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
The candidates of input constraints are presented in \ref{sec:appen:cstr}.

% ====================================
%  SECTION PROBLEM FORMULATION 
% ====================================
\section{Problem Formulation}\label{sec:Problem Formulation}

@@

The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model. The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.99\linewidth]{src/figures/DNN.drawio.pdf}
    \caption{
        Architecture of the DNN $\NN({\q}_n;\wth)$ with $2$ hidden layers.
    }
    \label{fig:DNN}
\end{figure}

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \act_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

%  SECTION SIMULATION ======================================
\section{Real-Time Implementation and Validation}\label{sec:sim}

The proposed CONAC was validated via real-time experiment on a two-link manipulator.

\subsection{Validation Setup}

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\color{red}
The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
The reference trajectory was generated using the same method as in the numerical simulation.
\color{black}

% ------------------------------------
% Robot Model and Ref. Trajectory
% ------------------------------------
The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
\MSRY{CORRECT HERE}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CONAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.

@@

% ------------------------------------
% Controllers: CONAC 
% ------------------------------------
\subsubsection*{Controller 1: (C$_1$) CONAC; proposed}

To handle the input saturation, the proposed CONAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    c_{\overline\tau_2}     
    =
    \tau_2-\overline\tau_2
    \le 0
    ,
    \;
    c_{\underline\tau_2} 
    =
    \underline\tau_2-\tau_2
    \le 0
    ,
    \;
    c_{\rbu}
    =
    \tfrac{1}{2}
    (
        \norm{\rbu}-\overline\tau
    )^2 
    <0
    ,
    \label{eq:sim:cstr:CONAC}
\end{equation}
where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CONAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.

@@

% ------------------------------------
% Controllers: Aux. system in CONAC-AUX
% ------------------------------------
\subsubsection*{Controller 2: (C$_2$) CONAC with auxiliary system}

@@

% ------------------------------------
% Controllers: CONAC with small beta
% ------------------------------------
\subsubsection*{Controller 3: (C$_3$) CONAC with small $\beta_i$}

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.
\MSRY{CAN Hz?}
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.

@@

% ------------------------------------
% Parameter Variation 
% ------------------------------------
% \begin{figure}[!t]      
%     \centering
%     {\includegraphics[width=\figSizeOneCol\linewidth]{
%         src/measurement/figures/Fig11.eps
%     }}
% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CONAC and CONAC-AUX across various parameter values.}
%     \label{fig:ctrl:result:var}
% \end{figure}

% \begin{table}[!t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
%     \centering
%     \begin{tabular}{c c c c}
%     \hline
%         \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
%     \hline
%     \hline
%     \textbf{CONAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
%     \hline
%     \textbf{CONAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
%     \hline
%     \end{tabular}
%     \label{table:ctrl:result:var}
% \end{table}

% ------------------------------------
% Controller Parameters
% ------------------------------------
% \begin{table}[t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Parameters of the controllers used in simulation}
%     \label{table:controller:params}
%     \centering
%     \begin{tabular}{c | c c c c c c c c c c c c c c}
%     \hline
%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
%     \hline
%     \hline
%         \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
%     % \hline
%         \bf{CONAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
%     \hline
%     \end{tabular}
% \end{table}

@@

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about 
$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.

@@

The tracking performance of CONAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.

@@

\subsubsection{Computational Time}
is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 0.5 ms, which is less than the sampling time of 4 ms. 
This indicates that the proposed CONAC can be implemented in real-time applications.

\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
    \caption{
        Computational time of CONAC and CONAC-AUX. 
    }
    \label{fig:ctrl:real:result:cmp:time}
  \end{figure}
